---
title: "Introduction to githubr"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{githubr}
  %\VignetteEngine{knitr::knitr}
---
### **AUTHOR**: _Brian M. Bot (brian.bot@sagebase.org)_

```{r loadClient, include=FALSE, eval=TRUE}
if( file.exists("~/.Rprofile") ){
  source("~/.Rprofile")
}
require(githubr)
token <- Sys.getenv('GITHUBRTOKEN')
if(token != ""){
  setGithubToken(token)
}
```

## Overview

[GitHub](https://www.github.com) has emerged as a very popular tool for collaborative code development in the software community. The utility of source code repositories expands far beyond use in professional software development. In fact, it has been shown to be extremely useful for a number of other endeavors. The purpose of this package is to provide an interface for users of R to have web-accessible access to their code directly within their R sessions.

## Setting your GitHub credentials

Users can use `githubr` without authenticating (anonymous calls to the API), however there are limits both to what can be accessed as well as the number of API calls allowed. Please see the [GitHub Developer docs](https://developers.github.com) for more information on anonymous use of the GitHub API.

For access to private repositories and/or to have an increased limit on the number of API calls, users should register a personal access token with the client via the `setGithubToken` function. Personal access tokens can be generated on your [GitHub settings page](https://github.com/settings/tokens). Give your token a meaningful name, like "githubr token" such that you can remember what it is being used for. Once you have called `setGithubToken`, the token passed to this function is then used for all subsequent calls to github api for the current R session.

#### via interactive authorization
```{r loadNotRun, include=TRUE, eval=FALSE}
require(githubr)
setGithubToken("myTokenFromGithub12345678")
```

#### via a hook in your .Rprofile
Include the following information in your `.Rprofile` located in your root directory. As this is sensitive information, _**make sure that this file is only visible to you**_.
```{r rProfile, include=TRUE, eval=FALSE}
setHook(
  packageEvent("githubr", "attach"),
  function(...){
    ## set my github authorization at package loading
    setGithubToken("myTokenFromGithub12345678")
  }
)
```

## Getting meta-information about a GitHub repository

#### from head of the master branch (default)
```{r getRepoDefault}
repo <- getRepo('brian-bot/githubr')
repo
```

#### from a specific branch
```{r getRepoBranch}
repoDev <- getRepo('brian-bot/githubr', ref='branch', refName='dev')
repoDev
```

#### from a specific commit
```{r getRepoCommit}
repoCommit <- getRepo("brian-bot/githubr", ref="commit", refName="9382e7191073c1a5dc554ec8b6658d07d405b89e")
repoCommit
```


## Sourcing a file from a GitHub repository

```{r sourceRepoFile}
sourceRepoFile(repoDev, "inst/misc/helloWorld.R")
```

## Retrieving a permlink from a GitHub file

```{r getPermlink}
getPermlink(repoDev, "inst/misc/helloWorld.R")
```

## Viewing a specific commit on GitHub

```{r view, eval=FALSE}
view(repoDev, "inst/misc/helloWorld.R")
```


## R sessionInfo()
```{r sessionInfo}
sessionInfo()
```
